\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{mathptmx}

\renewcommand{\familydefault}{\rmdefault}
\linespread{1.05}

% ---------- section formatting ----------
\titleformat{\section}{\normalfont\large\bfseries}{}{0pt}{}
\titlespacing{\section}{0pt}{1em}{0.2em}

\newcommand{\sectionline}{\vspace{0.2em}\hrule\vspace{0.4em}}

% ---------- lists ----------
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep,topsep=0pt,leftmargin=*}

\begin{document}
\thispagestyle{empty}

\begin{center}
  {\LARGE \textbf{Ben Mackert}}\\
  (303) 551-4217 \quad|\quad \href{mailto:benmackert@gmail.com}{benmackert@gmail.com} \quad|\quad Denver, CO\\
  \href{https://www.linkedin.com/in/ben-mackert/}{linkedin.com/in/ben-mackert}
\end{center}

%---------------------------
\section*{Education}
\sectionline

\textbf{University of Colorado Boulder}, Boulder, CO\\
\textit{B.S. Electrical and Computer Engineering} \hfill Expected May 2027\\
GPA 3.8, Dean’s List

%---------------------------
\section*{Technical Courses}
\sectionline

\begin{itemize}[leftmargin=*]
  \item Circuits I (A), Circuits II (A), Electronics Design Lab (A–)
  \item Data Structures (A), Prog. Digital Systems (A–), Physics II (A)
  \item Calculus I (A, AP 5), Calculus II (A–), Calculus III (A–)
\end{itemize}


%---------------------------
\section*{Skills}
\sectionline

\textbf{Languages:} C++, Python, RISC-V Assembly, Arduino, Verilog, LaTeX, Java, HTML, CSS

\textbf{Softwares:} Altium Designer, SolidWorks, LTspice, Arduino IDE, VS Code, GitHub, Excel

\textbf{Hardware \& Testing:} PCB Design, SMD, THT, Soldering, Oscilloscopes, Function Generators, DMM, Power Supplies

\textbf{Core Engineering Skills:} Circuit Design, Embedded Systems, Digital Logic, Algorithms

\textbf{Professional Skills:} Technical Communication, Team Collaboration, Presentation, Documentation


%---------------------------
\section*{Experience}
\sectionline

\textbf{Engineering Intern – CONMED Corporation} \hfill May 2025 -- Aug 2025

\begin{itemize}
  \item Designed and built an auto-calibration system (Arduino Nano Every + digital potentiometer) to map ESU voltages to resistance using a 4\textsuperscript{th}-degree polynomial.
  \item Designed a custom PCB in Altium for the calibration hardware, integrating a resistor ladder with MCU control.
  \item Created a Python GUI (Tkinter) and backend (serial comms + Matplotlib) to display real-time calibration plots.
  \item Reduced calibration error by 92.5\%, enabling full transformer compatibility and cutting manufacturing scrap.
  \item Simulated 3- and 4-point calibration in Python; achieved LMS errors as low as 1.76~$\Omega^2$ across transformer models.
  \item Delivered three Python tools for modeling and documented findings in an internal engineering report.
\end{itemize}




%---------------------------
\section*{Projects}
\sectionline

\textbf{STM32 Microcontroller PCB – Bluetooth \& USB-C}

\begin{itemize}
 \item Created a 4-layer PCB with STM32 MCU in Altium Designer, routing for Bluetooth and USB-C integration.
  \item Achieved 480 Mbps USB-C data and BLE telemetry for wireless diagnostics between devices in testing scenarios.
  \item Optimized high-speed signal routing against EMI by collaborating with 3 engineers on layout constraints and PCB stack-up.
  \item Engineered oscilloscope-based test methods, boosting debugging efficiency by 20\% and accelerating bring-up.
\end{itemize}

\textbf{Restaurant Review Backend App}

\begin{itemize}
  \item Built a modular data store in C++ to manage structured reviews, enabling filtered queries in under 100 ms.
  \item Optimized search performance using hash maps and binary search trees; improved throughput and load handling by 40\%.
  \item Managed Git repository with isolated feature branches; reviewed, tested, and merged 10 pull requests with clean commits.
  \item Refined user input and query handling across 4 iterative versions, cutting user-reported bugs by over 30\%.
\end{itemize}

\textbf{Home Security System – Arduino Prototype}

\begin{itemize}
  \item Developed a PIR-triggered security alarm using Arduino Uno, covering a 15 ft motion-detection zone with buzzer feedback.
  \item Soldered and assembled THT components onto a custom-designed PCB; passed 100-cycle stress and functionality test.
  \item Implemented motion detection logic with audible buzzer response and logged 50+ events via serial monitor.
  \item Delivered 3 successive PCB revisions with updated schematics and BOMs, improving reliability and reducing false triggers.
\end{itemize}


\end{document}
